%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Authors:
% Claud D. Park <posquit0.bj@gmail.com>
% Lars Richter <mail@ayeks.de>
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Configuration
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Themes: Awesome-CV
\documentclass[11pt, a4paper]{awesome-cv}

%%% Override a directory location for fonts(default: 'fonts/')
\fontdir[fonts/]

%%% Configure a directory location for sections
\newcommand*{\sectiondir}{cv/}

%%% Override color
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight
%% Color for highlight
% Define your custom color if you don't like awesome colors
\colorlet{awesome}{awesome-red}
%\definecolor{awesome}{HTML}{CA63A8}
%% Colors for text
%\definecolor{darktext}{HTML}{414141}
%\definecolor{text}{HTML}{414141}
%\definecolor{graytext}{HTML}{414141}
%\definecolor{lighttext}{HTML}{414141}

%%% Override a separator for social informations in header(default: ' | ')
%\headersocialsep[\quad\textbar\quad]


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Personal Data
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Essentials
\name{Boris}{Ermakov-Spektor}
\address{1810 NW 23rd Blvd Apt.236, Gainesville, Florida 32605}
\mobile{(305) 467-8502} 
%%% Social
\email{b.ermakovspektor@ufl.edu}
%\homepage{bspwr.com}
\github{BSpwr}
\linkedin{BSpwr}
%%% Optionals
\position{Computer Engineer{\enskip\cdotp\enskip}Software Developer}
%\quote{``Never stop pushing the limits."}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Letter Data (Cover Letter)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\recipient
  {University Relations Team}
  {Advanced Micro Devices, Inc.\\7171 Southwest Pkwy\\Austin, TX 78735}
\letterdate{\today}
%\lettertitle{Job Application for Software Engineer}
\letteropening{Dear Co-Op Recruiter,}
\letterclosing{Sincerely,}
\letterenclosure[Attached]{Résumé}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Content
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Make a footer for CV with three arguments(<left>, <center>, <right>)
\makecvfooter
  {\today}
  {Boris Ermakov-Spektor~~~·~~~Cover Letter}
  {}

\begin{document}
%%% Make a header for CV using personal data
\makecvheader

%%% Make a title for Cover Letter using letter data
\makelettertitle

%%% Write content for your cover letter
\begin{cvletter}
%\cvparagraph{About Me}
After perusing the Advanced Micro Devices careers website, the co-op as a validation engineer at AMD piqued my interest. In addition to my impressive academic standing as a sophomore studying computer engineering at the University of Florida, I have worked as a software and hardware contributor at AdMobilize in Miami, Florida, where I learned many pertinent skills that will make me a valuable asset at AMD. Apart from my internship experience, I have also developed leadership skills through my multitude of extracurricular activities.

%\cvparagraph{Pertinent Experience}
As a software and hardware contributor at AdMobilize, I performed testing and quality assurance to ensure that software modifications passed our continuous integration protocol. I also contributed to the development and optimization of our hardware construction protocol, gaining experience in prototyping. While at AdMobilize, I took the initiative of optimizing the software delivery process to devices, which led to immediate gains in speed and productivity. As such, I am well poised to perform hardware and software validation.

%\cvparagraph{Why AMD?}
AMD continues pushing boundaries, from bringing 64-bit chips to the masses to developing the revolutionary infinity fabric used in Ryzen. As a long time computer enthusiast, I greatly value AMD's culture of innovation and excellence. I am deeply interested in microprocessor technologies, and this co-op will provide me with the opportunity to develop my skills, and expand my knowledge. As an engineer at AMD, I will provide the same forward-thinking attitude that got AMD where it is today, and work to the utmost of my ability to solve tomorrow's challenging problems. I can be contacted by email or by phone to schedule an interview. Thank you for your consideration.

%\cvparagraph{Why ME?}

\end{cvletter}

%%% Make a closing for Cover Letter using letter data
\makeletterclosing

\end{document}
