%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Capital One} % Organization/group
    {Software Engineering Intern} % Affiliation/role
    {Richmond, Virginia, USA} % Location
    {June 2021 - Aug. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Implemented an agent management dashboard to recover failing agents on production cloud instances.}
        \item {Developed a GraphQL backend in Go to communicate with the agent API.}
        \item {Utilized Docker and Jenkins to create CI/CD pipeline to validate incoming PRs and build new images.}
        \item {Used Terraform to set up AWS configurations for deploying EC2 instances with an ALB.}
      \end{cvitems}
    }

%---------------------------------------------------------

%---------------------------------------------------------
\cventry
  {SHREC @ UF} % Organization/group
  {Undergraduate Research Assistant} % Affiliation/role
  {Gainesville, Florida, USA} % Location
  {Feb. 2021 - PRESENT} % Date(s)
  {
    \begin{cvitems} % Description(s) of experience/contributions/knowledge
      \item {Implemented a pipelined 4-parallel FFT in VHDL.}
      \item {Utilized Python to generate and validate test data for VHDL testbench.}
      \item {Wrote automated VHDL testbenches to test for component correctness.}
      \item {Benchmark CUDA vs DPC++ (OneAPI) performance for GPU compute.}
    \end{cvitems}
  }

%---------------------------------------------------------

%---------------------------------------------------------
  \cventry
    {Ultimate Kronos Group} % Organization/group
    {Software Engineering Intern} % Affiliation/role
    {Weston, Florida, USA} % Location
    {Jan. 2021 - April 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Implemented various features for filtering Kafka messages using Java.}
        \item {Refactored a CLI in Go to add crucial new functionality.}
        \item {Dockerized a NodeJS application and automated image building for deployment to the cloud.}
      \end{cvitems}
    }

%---------------------------------------------------------

%---------------------------------------------------------
  \cventry
    {UF CISE \& ECE} % Organization/group
    {Undergraduate Teaching Assistant} % Affiliation/role
    {Gainesville, Florida, USA} % Location
    {Jan. 2019 - PRESENT} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Former teaching assistant for Computer Organization, Data Structures, and Digital Logic.}
        \item {Current teaching assistant for Operating Systems.}
        \item {Held office hours, taught lab sections, created guides, led discussion sections.}
      \end{cvitems}
    }

%---------------------------------------------------------

%---------------------------------------------------------
  \cventry
    {Matrix Labs} % Organization
    {Software Engineering Intern} % Job title
    {Miami, Florida, USA} % Location
    {May. 2019 - Aug. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Enabled NFC support for the MATRIX platform through designing and developing a C++ abstraction.}
        \item {Contributed to MATRIX community with up to date documentation.}
        \item {Conducted QA testing for crucial services.}
      \end{cvitems}
    }

%---------------------------------------------------------

%---------------------------------------------------------
  \cventry
    {AdMobilize} % Organization
    {Software Engineering Intern} % Job title
    {Miami, Florida, USA} % Location
    {May. 2018 - Aug. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Created the majority of end-user documentation with examples in Markdown for entire C++ API.}
        \item {Wrote scripts in Bash for improving device provisioning and setup, reducing deployment time by half.}
        \item {Added user-facing features to C++ API, simplifying user experience.}
        \item {Worked with development team to help implement and test improvements to mission-critical software in Node.JS.}
      \end{cvitems}
    }

%---------------------------------------------------------
  % \cventry
  %   {AdMobilize} % Organization
  %   {Hardware Contributor} % Job title
  %   {Miami, Florida, USA} % Location
  %   {Aug. 2015 - Jul. 2017} % Date(s)
  %   {
  %     \begin{cvitems} % Description(s) of tasks/responsibilities
  %       \item {Optimized deployment of software onto Linux-based devices by using cloning - speeding up deployment by 50\%.}
  %       \item {Lead inventory management and device assembly.}
  %       \item {Wrote in-house documentation detailing device assembly.}
  %       \item {Developed and tested improvements in device assembly that allowed for speedups of 20\%.}
  %     \end{cvitems}
  %   }

%---------------------------------------------------------
\end{cventries}
