%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Matrix Labs} % Organization
    {Software Contributor} % Job title
    {Miami, Florida, USA} % Location
    {May. 2019 - Aug. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Enabled NFC support for the MATRIX platform, enabling ease of use through a C++ abstraction.}
        \item {Contributed to MATRIX community with up to date documentation.}
        \item {Conducted QA testing for crucial services.}
      \end{cvitems}
    }

%---------------------------------------------------------

%---------------------------------------------------------
  \cventry
    {AdMobilize} % Organization
    {Software Contributor} % Job title
    {Miami, Florida, USA} % Location
    {May. 2018 - Jun. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Created the majority of end-user documentation with examples  in Markdown for entire C++ API.}
        \item {Configured Linux and Windows base systems for deployment.}
        \item {Wrote scripts in Bash for improving device provisioning and setup, reducing deployment time by half.}
        \item {Added user-facing features to C++ API, simplifying user experience.}
        \item {Conducted thermal testing on SOC's for product design.}
        \item {Worked with development team to help implement and test improvements to mission-critical software.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Admobilize} % Organization
    {Hardware Contributor} % Job title
    {Miami, Florida, USA} % Location
    {Aug. 2015 - Jun. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Optimized deployment of software onto Linux-based devices.}
        \item {Lead inventory management and device assembly.}
        \item {Wrote in-house documentation detailing device assembly.}
        \item {Developed and tested improvements in device assembly.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}